Staged Abstract Interpreters

### 2019-04-05 paper/70_eval.tex
typo

\paragraph{Implementation and Evaluation Environment}
We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis focus on lambda terms in functional languages. A frontend
desugars Scheme to a small core language that make the analyzer easy to
implement. As described in Section \ref{cfa}, we implement a monovariant
0-CFA-like analysis, \todo{a context-sensitive $1$-CFA-like analysis, both their
  versions with and without store-widening}. We also implement several
optimizations mentioned in Section \ref{staged_ds} (less than ~30 LOC in total).

@@

\paragraph{Benchmarks}
The benchmark programs we used in the experiment are collected from several
previous papers \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and exisiting artifacts
\footnote{https://github.com/ilyasergey/reachability} for control-flow analysis.
Some of the benchmarks are small programs designed for experiments, such as the
@kcfa-worst-@$n$ series, which are intended to challenge $k$-CFA; while some
other benchmarks are from real-world applications, for examples, the RSA public
key encryption algorithm @rsa@. In the Figure \ref{evaluation_result}, we report
the number of AST node after parsing and desugaring (excluding comments) as a
proper measurement of program size.

@@

We also observe that much overhead of unstaged analyzers are from the monadic
layers. Thus our evaluation result provides an abstraction without regret
approach to construct optimizing abstract interpreters -- user may write an
high-level modular and composable abstract interpreter, and then derive a staged
version in a principled way that runs significantly faster.

>>>>

\paragraph{Implementation and Evaluation Environment}
We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis focus on lambda terms in functional languages. A front-end
desugars Scheme to a small core language that make the analyzer easy to
implement. As described in Section \ref{cfa}, we implement a monovariant
0-CFA-like analysis, \todo{a context-sensitive $1$-CFA-like analysis, both their
  versions with and without store-widening}. We also implement several
optimizations mentioned in Section \ref{staged_ds} (less than ~30 LOC in total).

@@

\paragraph{Benchmarks}
The benchmark programs we used in the experiment are collected from several
previous papers \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and existing artifacts
\footnote{https://github.com/ilyasergey/reachability} for control-flow analysis.
Some of the benchmarks are small programs designed for experiments, such as the
@kcfa-worst-@$n$ series, which are intended to challenge $k$-CFA; while some
other benchmarks are from real-world applications, for examples, the RSA public
key encryption algorithm @rsa@. In the Figure \ref{evaluation_result}, we report
the number of AST node after parsing and desugaring (excluding comments) as a
proper measurement of program size.

@@

We also observe that much overhead of unstaged analyzers are from the monadic
layers. Thus our evaluation result provides an abstraction without regret
approach to construct optimizing abstract interpreters -- user may write a
high-level modular and composable abstract interpreter, and then derive a staged
version in a principled way that runs significantly faster.
